\documentclass[a4paper,10pt]{article}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{left=1in, right=1in, top=1in, bottom=1in}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=cyan,
}

\setlength{\parskip}{0.5em}
\setlength{\parindent}{0em}

% Define colors
\definecolor{primary}{RGB}{41,128,185}
\definecolor{secondary}{RGB}{44,62,80}

\begin{document}

% Header
\begin{center}
    {\Huge \textbf{Jamshid K}} \\
    \vspace{2mm}
    \textcolor{primary}{\Large \textbf{ Odoo Technical Architect}} \\
    \vspace{2mm}
    (+966) 561276465 \\
    \href{mailto:jamshu.mkd@gmail.com}{jamshu.mkd@gmail.com} \\
    Saudi Arabia, Jeddah \\
    \href{https://www.linkedin.com/in/jamshid-k-72758aa2/}{linkedin.com/in/jamshid-k-72758aa2/}
\end{center}

\vspace{5mm}

% Professional Summary
\section*{\textcolor{primary}{Professional Summary}}
\noindent I am an innovative system architect with 11+ years of experience and a demonstrated track record of delivering cutting-edge technology solutions and business transformations for highly reputed organizations. I have proven success in leading high-performance teams as well as defining, building, and optimizing best-in-class business solutions. My leadership style encourages employee development, resulting in ultimate performance, motivation, and dedication while effectively managing day-to-day operations.

\vspace{5mm}

% Work Experience
\section*{\textcolor{primary}{Work Experience}}

\begin{itemize}[left=0pt, label=$\vcenter{\hbox{\tiny$\bullet$}}$]
    \item \textbf{ULTS - Calicut} \hfill \textbf{06/2023-03/2025} \\
    \textit{System Architect} \\
    \begin{itemize}[left=5pt, label=$\vcenter{\hbox{\tiny$\bullet$}}$]
        \item Spearheaded the design and implementation of scalable architecture solutions, enhancing system reliability.
        \item Mentored a team of 25+ developers, leading to improvement in project delivery time.
        \item Integrated advanced technologies, resulting in reduction in operational costs.
    \end{itemize}

    \item \textbf{Zeeve Deep Tech - Delhi} \hfill \textbf{12/2021-05/2023} \\
    \textit{Team Lead} \\
    \begin{itemize}[left=5pt, label=$\vcenter{\hbox{\tiny$\bullet$}}$]
        \item Led a cross-functional team of 8+ professionals in the development of blockchain-based applications.
        \item Enhanced system performance by optimizing code,reducing downtime.
        \item Collaborated with stakeholders to define project goals, ensuring alignment with business objectives.
    \end{itemize}

    \item \textbf{AL Khidma Systems - Kochi} \hfill \textbf{11/2020-12/2021} \\
    \textit{Team Lead} \\
    \begin{itemize}[left=5pt, label=$\vcenter{\hbox{\tiny$\bullet$}}$]
        \item Managed a team of developers in the creation of custom Odoo modules, improving client satisfaction.
        \item Streamlined development processes, leading to increase in productivity.
    \end{itemize}

    \item \textbf{Beta Information Technology - Dubai} \hfill \textbf{12/2017-03/2020} \\
    \textit{Senior Developer} \\
    \begin{itemize}[left=5pt, label=$\vcenter{\hbox{\tiny$\bullet$}}$]
        \item Developed and deployed enterprise-grade applications, resulting increase in system efficiency.
        \item Played a key role in migrating legacy systems to modern platforms, improving scalability.
    \end{itemize}

    \item \textbf{Orchid Infosys - Dubai} \hfill \textbf{03/2015-11/2017} \\
    \textit{Senior Developer} \\
    \begin{itemize}[left=5pt, label=$\vcenter{\hbox{\tiny$\bullet$}}$]
        \item Led the development of robust, secure software solutions for various clients.
        \item Implemented best practices in software engineering, reducing code defects.
    \end{itemize}

    \item \textbf{Novizco Infotech - Kochi} \hfill \textbf{07/2013-12/2014} \\
    \textit{Python Odoo Developer} \\
    \begin{itemize}[left=5pt, label=$\vcenter{\hbox{\tiny$\bullet$}}$]
        \item Developed Odoo-based applications, contributing to improvement in data processing speed.
        \item Collaborated with cross-functional teams to deliver projects on time and within budget.
    \end{itemize}
\end{itemize}

\vspace{5mm}


% Projects
\section*{\textcolor{primary}{Selected Projects}}

\textbf{Redis Integration with Odoo POS 16 } \\
\textit{Role: System Architect | Technologies Used: Redis, Odoo, Python} \\
Led the integration of Redis with Odoo POS 16 to optimize product loading times in the POS configuration. This enhancement significantly reduced the loading time of POS sessions , improving overall efficiency and user experience for large-scale retail operations.

\vspace{3mm}

\textbf{Supermarket POS using Odoo POS} \\
\textit{Role: System Architect | Technologies Used: Odoo, Python} \\
Designed and implemented a custom POS system tailored for a super market using Odoo POS. The solution included features for managing inventory, handling various payment methods, and ensuring compliance with industry regulations, enhancing the shop's operational efficiency.

\vspace{3mm}

\textbf{Medical Shop Retail and Warehouse Sales Using Odoo} \\
\textit{Role: System Architect | Technologies Used: Odoo, Python} \\
Developed and implemented a comprehensive solution for managing retail and warehouse operations in a medical shop using Odoo. The system streamlined inventory management, order processing, and sales tracking, significantly improving operational efficiency and inventory accuracy.

\vspace{3mm}

\textbf{Carbon Certificate Market with Odoo and Flask Using Blockchain Technology} \\
\textit{Role: System Architect | Technologies Used: Odoo, Flask, Blockchain, Node.js} \\
Architected a Carbon Certificate Market platform integrating Odoo with Flask and blockchain technology using Node.js. The platform enabled secure and transparent trading of carbon certificates, leveraging blockchain for immutable records and smart contracts, ensuring compliance and enhancing market trust.

\vspace{3mm}

\textbf{Hanveev Manufacturing Process with Odoo} \\
\textit{Role: System Architect | Technologies Used: Odoo, Python} \\
Implemented a comprehensive manufacturing management system for Hanveev using Odoo. The system optimized the production processes, from raw material procurement to finished goods, ensuring efficient workflow management, inventory control, and production tracking.

\vspace{3mm}

\textbf{SCF Interswitch Blockchain-based Online Bill Payment via Bank} \\
\textit{Role: Team Lead | Technologies Used: Odoo, Node.js, Blockchain, Django} \\
Led the development of a blockchain-based vendor bill payment system that allowed banks to immediately pay bills after verifying documents. The system enabled vendors to receive payments quickly while allowing customers to repay the bank at a later date. The solution integrated Odoo, Node.js, and Django to ensure seamless operation and security.

\vspace{3mm}

\textbf{Project Management Application} \
\textit{Role: Senior Developer | Technologies Used: Odoo, Python} \\
Developed a comprehensive project management application using Odoo technology. The system included engineer KPI tracking, analytic accounting for project expenses, and revenue recognition features. This solution enabled precise monitoring of project performance, improved resource allocation, and enhanced financial reporting accuracy. 

\vspace{3mm}

\textbf{Gulf Seafood Manufacturing} \
\textit{Role: Senior Developer | Technologies Used: Odoo, Python} \\
Developed a comprehensive application for a seafood manufacturing company using Odoo technology. The system integrated manufacturing processes, inventory management with specialized features for perishable goods, and detailed financial accounting.

\vspace{3mm}

\textbf{Fleet Management System} \
\textit{Role: Developer | Technologies Used: Odoo, Python} \\
Developed a comprehensive fleet management system using Odoo technology. The solution streamlined vehicle operations, maintenance, and cost management for a large-scale transportation company. 

\vspace{5mm}

% Education
\section*{\textcolor{primary}{Education}}
\textbf{B.Tech in Information Technology} \\
Govt. Engineering College, Sreekrishnapuram, Palakkad, 2013.

\vspace{5mm}

% Skills
\section*{\textcolor{primary}{Skills}}
\textbf{Technical Skills:} Python,Go, Javascript, Odoo, Odoo.sh Django, AWS, Git, Redis, RabbitMQ, Celery, Docker, GitHub, Node, Svelte JS \\
\textbf{Soft Skills:} Leadership, Team Management, Strategic Planning, Problem-Solving

\vspace{5mm}

% Certifications and Licenses
\section*{\textcolor{primary}{Certifications and Licenses}}
\begin{itemize}[left=0pt, label=$\bullet$]
    \item AWS Solution Architect Associates
    \item Odoo 17 Functional Certification
    \item Odoo 13 Functional Certification
\end{itemize}

\vspace{5mm}

% Languages
\section*{\textcolor{primary}{Languages}}
English, Hindi, Tamil, Malayalam

\vspace{5mm}



% Footer
\section*{\textcolor{primary}{Interests}}
\begin{itemize}[left=0pt, label=$\vcenter{\hbox{\tiny$\bullet$}}$]
    \item Artificial Intelligence and Machine Learning
    \item Blockchain Technology
    \item Reading Tech Blogs and Journals
    \item Mentoring and Coaching
\end{itemize}

\end{document}

